Conversations in time: interactive visualization to explore structured temporal data

### 2020-08-04 tsibbletalk.Rmd
minor tweaks

The `spec` argument in the `as_shared_tsibble()` function takes a symbolic formula to allow users to specify structural combinations, using `/` and `*` adopted from Wilkinson notation (10.2307/2346786) for nesting and crossing respectively.

>>>>

The `spec` argument in the `as_shared_tsibble()` function takes a symbolic formula to allow users to specify structured combinations, using `/` and `*` adopted from Wilkinson notation (10.2307/2346786) for nesting and crossing expressions respectively. By default, the specification assumes crossing structure for all units.

Specifying the structure is particularly useful when there's nesting structure in the data.

### 2020-08-04 tsibbletalk.tex
minor tweaks

The \texttt{spec} argument in the \texttt{as\_shared\_tsibble()}
function takes a symbolic formula to allow users to specify structural
combinations, using \texttt{/} and \texttt{*} adopted from Wilkinson
notation (10.2307/2346786) for nesting and crossing respectively.

>>>>

The \texttt{spec} argument in the \texttt{as\_shared\_tsibble()}
function takes a symbolic formula to allow users to specify structured
combinations, using \texttt{/} and \texttt{*} adopted from Wilkinson
notation (10.2307/2346786) for nesting and crossing expressions
respectively. By default, the specification assumes crossing structure
for all units.

Specifying the structure is particularly useful when there's nesting
structure in the data.
